Fusion Moves for Correlation Clustering

### 2015-03-17 paper/datasets.tex
added joergs newest bibtex ref

\textbf{Network Modularity Clustering.}
As another example for network clustering we use the \emph{modularity-clustering} models from~\cite{kappes_2014_benchmark_arxiv} which are small but fully connected.

@@

We use the publicly available benchmark instances from~\cite{kappes_2013_benchmark_cvpr,kappes_2014_benchmark_arxiv}.
For 2D images from the Berkeley Segmentation Database~\cite{martin_2001}, we took the segmentation problems called \emph{image-seg}~\cite{andres_2011_iccv,kappes_2013_benchmark_cvpr}.
For 3D volume segmentation we use the models \emph{knott-3d-150}, \emph{-300} and \emph{-450} from~\cite{kroeger_2012_eccv,kappes_2014_benchmark_arxiv} as well as the large
instance from the \emph{3d-seg} model~\cite{andres_2011_iccv,kappes_2013_benchmark_cvpr}. These instances have underlying cube sizes of  $150^3$, $300^3$, $450^3$, and $900^3$, respectively.
We also requested larger instances from the authors of~\cite{kroeger_2012_eccv} who kindly provided us the dataset~\emph{knott-3d-550} with cube size  $550^3$.
%More information of the size of instances is given in Tab.~\ref{tab:instance_sizes}.

>>>>

\textbf{Network Modularity Clustering.}
As another example for network clustering we use the \emph{modularity-clustering} models from~\cite{kappes-2015-ijcv} which are small but fully connected.

@@

We use the publicly available benchmark instances from~\cite{kappes_2013_benchmark_cvpr,kappes-2015-ijcv}.
For 2D images from the Berkeley Segmentation Database~\cite{martin_2001}, we took the segmentation problems called \emph{image-seg}~\cite{andres_2011_iccv,kappes_2013_benchmark_cvpr}.
For 3D volume segmentation we use the models \emph{knott-3d-150}, \emph{-300} and \emph{-450} from~\cite{kroeger_2012_eccv,kappes-2015-ijcv} as well as the large
instance from the \emph{3d-seg} model~\cite{andres_2011_iccv,kappes_2013_benchmark_cvpr}. These instances have underlying cube sizes of  $150^3$, $300^3$, $450^3$, and $900^3$, respectively.
We also requested larger instances from the authors of~\cite{kroeger_2012_eccv} who kindly provided us the dataset~\emph{knott-3d-550} with cube size  $550^3$.
%More information of the size of instances is given in Tab.~\ref{tab:instance_sizes}.
